{\fontfamily{ptm}\selectfont Reading Notes}

### 2025-05-09 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
>w<, changes

@@

                We define $F$ to be $q$ weakly convex if there exists $q \in \RR$ such that the function $F + q/2\Vert \cdot\Vert^2$ is a convex function and $q$ is the infimum of all such possible parameters. 

@@

@@

    \section{FISTA made simple}
        We make the proofs for FISTA  with common enhancement technique available in simple proofs. 
        We showcase the theories using a generic similar triangle representations of the algorithm which tremendously simplifies the arguments.

@@

        % ======================================================================
        % THEOREM | GENERIC GMAPG CONVERGENCE IN FXN VAL
        % ======================================================================

@@

        % ======================================================================
        % THEOREM | GENERIC GMAPG GRADIENT MAPPING CONVERGENCE
        % ======================================================================

@@

@@

            \begin{algorithmic}[1]\label{alg:armijo-ls}

@@

                    % \textbf{Function ArmijoLS}
                    % $(f, g, x, v, L, \alpha, \_, \_)$

@@

                        $g: \RR^n \rightarrow \overline \RR$  &  Convex function with Proximal operator\\ 

@@

                \STATE{\textbf{Return:} $y^+, x^+, \alpha^+, L^+$}
                \caption{Armijo Line Search}

@@

@@

            \begin{algorithmic}[1]\label{alg:chambolle-btls}

@@

                    % \textbf{Function ChamBT}($f, g, x, v, L, \alpha, L_{\min}, \rho$)
                    \textbf{Function ChamBT input: }

@@

                        $g:\RR^n \rightarrow \overline\RR$ & Convex with Proximal Operator\\ 

@@

                \STATE{\textbf{Return: }$y^+, x^+, \alpha^+, L^+$}
                \caption{Chambolle's Backtracking}

@@

        % BECK'S MONO ----------------------------------------------------------

@@

            \begin{algorithmic}[1]\label{alg:beck-mono}

@@

                        $\rho$ & Number $\rho \in (0, 1)$

@@

                \STATE{\textbf{Return: } $x^+, \eta$}
                \caption{Beck's monotone routine}

@@

        % NES'S MONO -----------------------------------------------------------

@@

@@

                \WHILE{$F(x^+) - F(\hat y) > -1/(2\eta)\Vert \mathcal G_{1/\eta}(\hat y)\Vert^2$}

@@

                \ENDWHILE

@@

                \caption{Nesterov's monotone routine}
            \end{algorithmic}\label{alg:nes-mono}

@@

        % GMAPG ----------------------------------------------------------------

@@

                        $f:\RR^n \rightarrow \RR$ &  Weakly Convex Lipschitz Smooth \\

@@

@@

                        $r_{\min} $ & $r_{\min} \in (0, 1)$ \\ 

@@

                        $\mathbb L_{\mathcal S}$ \\ Algorithm \ref{alg:armijo-ls} or \ref{alg:chambolle-btls}

@@

                \STATE{\textbf{Return: }}

@@

        % ======================================================================
        % EXAMPLE | NESTEROV'S MONOTONE SCHEME WITH GENERIC LINE SEARCH
        % ======================================================================

@@

    \section{Practical enhancement from the Nesterov's Monotone Variant}
        Firstly, we will introduce some theories in for nonconvex functions. 
        This is necessary because Nesterov's monotone variants can adapt to weakly convex objective functions. 
        The following assumption will characterize the full scope of discussion in nonconvexity objective function.

        \begin{definition}[nonconvex Nesterov's monotone scheme]\;\label{def:nes-monotone-scheme}\\

>>>>

                If a function is $L$ smooth, it also be $L$ weakly convex. 
                Here we defined $q_f$ because the actual weakly convex constant may be much smaller than $L$, and it is true in the case when $g$ is in fact convex.  

@@

                We define $F$ to be $q$ weakly convex if there exists $q \in \ge 0$ such that the function $F + q/2\Vert \cdot\Vert^2$ is a convex function and $q$ is the infimum of all such possible parameters. 

@@

                If $q = 0$, $f$ is convex or strongly convex. 

@@

    \section{FISTA made simple}
        We make the proofs for FISTA  with common enhancement technique available in simple proofs. 
        We showcase the theories using a generic similar triangle representations of the algorithm which tremendously simplifies the arguments. 

@@

@@

@@

        \subsection{Line search routines}
            % ARMIJO LINE SEARCH -----------------------------------------------

@@

@@

@@

                            $g: \RR^n \rightarrow \overline \RR$  &  Convex\\ 

@@

                    \STATE{\textbf{Return:} $x^+, y^+, \alpha^+, L^+$}
                    \caption{Armijo Line Search}\label{alg:armijo-ls}

@@

            % CHAMBOLLE'S BACKTRACKING LINE SEARCH -----------------------------

@@

@@

                        \textbf{Function ChamBT Inputs: }

@@

                            $g:\RR^n \rightarrow \overline\RR$ & Convex\\ 

@@

                    \STATE{\textbf{Return: }$x^+, \alpha^+, L^+$}
                    \caption{Chambolle's Backtracking}\label{alg:chambolle-btls}

@@

        \subsection{Monotone routines}
            % BECK'S MONO ------------------------------------------------------

@@

@@

                            $\rho$ & Number $\rho \in (0, 1)$ \\
                            $G \in \RR$ & Number 

@@

                    \STATE{\textbf{Return: } $x^+, x_{k - 1} ,\eta$}
                    \caption{Beck's monotone routine}\label{alg:beck-mono}

@@

            % NES'S MONO -------------------------------------------------------

@@

                            $G \in \RR$  & Number

@@

                    \FOR {i = 1, 2, \ldots, 53}
                        \IF{$(f + g)(x^+) - (f + g)(\hat y) \le -1/(2\eta)\Vert \mathcal G_{1/\eta}(\hat y)\Vert^2$}
                            \STATE{\textbf{Break}}

@@

                            \STATE{$x^+ := T_{1/\eta}(\hat y)$.}
                    \STATE{$G := \eta (x^+ - \hat y).$}

@@

                    \caption{Nesterov's monotone routine}\label{alg:nes-mono}

@@

        \subsection{GMAPG main algorithm}
            % GMAPG ------------------------------------------------------------

@@

                            $f:\RR^n \rightarrow \RR$ & Lipschitz Smooth \\

@@

                            $x_{-1}$ & Vector\\

@@

                            $r $ & $r \in (0, 1)$ \\ 

@@

                            $\epsilon \in \RR$ & Number\\
                            $\mathbf L$ & Algorithm \ref{alg:armijo-ls} or \ref{alg:chambolle-btls}\\
                            $\mathbf M$ & Algorithm \ref{alg:beck-mono} or \ref{alg:nes-mono}\\
                            $\mathbf E_\chi$ & Exit Condition 

@@

                    \STATE{$\alpha_0 := 1$.}
                    \STATE{$x_0, y_0,\alpha_1, L_0 := \textbf{ArmijoLS}(f, g, x_{-1}, x_{-1}, L, \alpha_0)$.}
                    \STATE{$\eta_0 := L_0; v_0 := x_0; G_0 = L_0(x_0 - y_0).$}
                    \FOR{$k := 1, 2,\ldots, N$}
                            $\tilde x_{k}, y_k, \alpha_{k + 1}, L_{k} := \mathbf{L}(f, g, v_{k - 1}, x_{k - 1}, L_{k - 1}, \alpha_{k}, rL_{k - 1}, \rho)$.
                            $\rho := \rho^{1/2} \textbf{ if } L_{k} > L_{k - 1} \textbf{ else } \rho$.
                        \STATE{$G_k:= L_k(\tilde x_k - y_k)$}
                            $x_k, \hat y_k, \eta_{k + 1}, G_k := \mathbf M(f, g, \tilde x_k, x_{k - 1}, \eta_k, G_k)$.
                        \IF{$G_k < \epsilon \textbf{ or } (\mathbf E_\chi  \textbf{ and } k > N_{\min})$}
                    \STATE{\textbf{Return: }$x_k, k$}

@@

@@

    \section{Practical enhancement from the Nesterov's Monotone Variant}
        Firstly, we will introduce some theories in for nonconvex functions. 
        This is necessary because Nesterov's monotone variants can adapt to weakly convex objective functions. 
        The following assumption will characterize the full scope of discussion in nonconvexity objective function. 
        \begin{definition}[nonconvex Nesterov's monotone scheme]\;\label{def:nes-monotone-scheme}\\
